Dynamics of isoflurane-induced vasodilation and blood flow of cerebral vasculature revealed by multi-exposure speckle imaging

### 2021-10-28 article.tex
Report F-statistic with ANOVAs

The percent changes in vessel diameter and blood flow between the awake and anesthetized states were aggregated across all subjects and imaging sessions as shown in Fig.~\ref{fig:aggregated}. The anesthetized measurements for Subject 1, which underwent the extending imaging sessions, were taken at $t \approx 80$ minutes to match the timing of the other subjects (20 minutes after the start of anesthesia). A total of 108 measurements were included in the analysis (33 arteries, 29 veins, 46 parenchyma regions). Similar to the results seen in Fig.~\ref{fig:timecourse}, the vasodilatory effects of isoflurane induced large changes in the cortical hemodynamics. On average, vessel width increased by 14.1\%, with arteries increasing by 15.0\% and veins increasing by 13.0\% (Fig.~\ref{fig:aggregated}a). There was no significant difference in the percent change in width between arteries and veins ($p = 0.61$). Vascular flux increased, on average, by 96.0\%, with arteries increasing by 81.7\% and veins increasing by 112.2\% (Fig.~\ref{fig:aggregated}b). Parenchymal tissue perfusion increased by 84.7\%. While the ANOVA was significant ($p = 0.041$), the multiple pairwise comparisons between arteries, veins, and parenchyma regions were all non-significant ($p > 0.05$).

% Figure 3 - Aggregated Awake to Anesthetized Results
\begin{figure}
    \includegraphics[width=\textwidth]{Figure3.pdf}
    \caption {
        (a) Percent change in vessel diameter for arteries and veins between the awake and anesthetized states ($p > 0.05$). (b) Percent change in arterial and venous vascular flux and parenchymal tissue perfusion between the awake and anesthetized states ($p > 0.05$). Measurements in both charts aggregated across all subjects and all imaging sessions.
    }
    \label{fig:aggregated}
\end{figure}

The dynamics of the isoflurane-induced flow changes in Subject 1 can be seen in the blood flow rise time map in Fig.~\ref{fig:risetime}a. $ICT$ values across the entire field-of-view increased by at least 50\% in just over one minute following the start of anesthesia. The vasculature, including both arteries and veins, appears to change flow faster than parenchyma regions. However, upon aggregating ROI measurements across all subjects and imaging sessions (Fig.~\ref{fig:risetime}b), arteries have significantly faster rise times ($40.5$ seconds) compared to veins ($50.7$ seconds, $p = \num{3.7e-6}$) or parenchyma regions ($46.1$ seconds, $p = 0.006$). Parenchymal regions also have significantly faster rise times than veins ($p = 0.043$).

>>>>

The percent changes in vessel diameter and blood flow between the awake and anesthetized states were aggregated across all subjects and imaging sessions as shown in Fig.~\ref{fig:aggregated}. The anesthetized measurements for Subject 1, which underwent the extending imaging sessions, were taken at $t \approx 80$ minutes to match the timing of the other subjects (20 minutes after the start of anesthesia). A total of 108 measurements were included in the analysis (33 arteries, 29 veins, 46 parenchyma regions). Similar to the results seen in Fig.~\ref{fig:timecourse}, the vasodilatory effects of isoflurane induced large changes in the cortical hemodynamics. On average, vessel width increased by 14.1\%, with arteries increasing by 15.0\% and veins increasing by 13.0\% (Fig.~\ref{fig:aggregated}a). There was no significant difference in the percent change in width between arteries and veins ($F_{(1,60)} = 0.27$, $p = 0.61$). Vascular flux increased, on average, by 96.0\%, with arteries increasing by 81.7\% and veins increasing by 112.2\% (Fig.~\ref{fig:aggregated}b). Parenchymal tissue perfusion increased by 84.7\%. While the one-way ANOVA was significant ($F_{(2,105)} = 0.27$, $p = 0.041$), the multiple pairwise comparisons between arteries, veins, and parenchyma regions were all non-significant ($p > 0.05$).

% Figure 3 - Aggregated Awake to Anesthetized Results
\begin{figure}
    \includegraphics[width=\textwidth]{Figure3.pdf}
    \caption {
        (a) Percent change in vessel diameter for arteries and veins between the awake and anesthetized states ($p > 0.05$). (b) Percent change in arterial and venous vascular flux and parenchymal tissue perfusion between the awake and anesthetized states (Pairwise comparisons all $p > 0.05$). Measurements in both charts aggregated across all subjects and all imaging sessions.
    }
    \label{fig:aggregated}
\end{figure}

The dynamics of the isoflurane-induced flow changes in Subject 1 can be seen in the blood flow rise time map in Fig.~\ref{fig:risetime}a. $ICT$ values across the entire field-of-view increased by at least 50\% in just over one minute following the start of anesthesia. The vasculature, including both arteries and veins, appears to change flow faster than parenchyma regions. However, upon aggregating ROI measurements across all subjects and imaging sessions (Fig.~\ref{fig:risetime}b) and finding a statistically significant one-way ANOVA ($F_{(2,105)} = 13.4$, $p = \num{6.5e-6}$), arteries have significantly faster rise times ($40.5$ seconds) compared to veins ($50.7$ seconds, $p = \num{3.7e-6}$) or parenchyma regions ($46.1$ seconds, $p = 0.006$). Parenchyma regions also have significantly faster rise times than veins ($p = 0.043$).
